\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-08-30 doc/USER_MANUAL/02_getting_started.tex
added Masaru Nagaso as author, and added Windows installation information

To download the SPECFEM3D\_Cartesian software package, type this:
\begin{verbatim}
git clone --recursive --branch devel https://github.com/geodynamics/specfem3d.git
\end{verbatim}
%
\noindent
We recommend that you add {\texttt{ulimit -S -s unlimited}} to your
{\texttt{.bash\_profile}} file and/or {\texttt{limit stacksize
unlimited }} to your {\texttt{.cshrc}} file to suppress any potential
limit to the size of the Unix stack.\\

@@

If you have problems configuring the code on a Cray machine, i.e. for instance if you get an error message from the \texttt{configure} script, try exporting these two variables:
\texttt{MPI\_INC=\${CRAY\_MPICH2\_DIR}/include and FCLIBS=" "}, and for more details if needed you can refer to the \texttt{utils/Cray\_compiler\_information} directory.

>>>>

To download the SPECFEM3D\_Cartesian software package, type this:
\begin{verbatim}
git clone --recursive --branch devel https://github.com/geodynamics/specfem3d.git
\end{verbatim}
%
\noindent
\red{Note: for people who would like to run the package on Windows rather than on Unix machines, you can install Docker or VirtualBox (installing a Linux in VirtualBox in that latter case) and run it easily from inside that.}\\

\noindent
We recommend that you add {\texttt{ulimit -S -s unlimited}} to your
{\texttt{.bash\_profile}} file and/or {\texttt{limit stacksize
unlimited }} to your {\texttt{.cshrc}} file to suppress any potential
limit to the size of the Unix stack.\\

@@

If you have problems configuring the code on a Cray machine, i.e. for instance if you get an error message from the \texttt{configure} script, try exporting these two variables:
\texttt{MPI\_INC=\${CRAY\_MPICH2\_DIR}/include and FCLIBS=" "}, and for more details if needed you can refer to the \texttt{utils/Cray\_compiler\_information} directory.
You can also have a look at the configure script called \texttt{utils/Cray\_compiler\_information/configure\_SPECFEM\_for\_Piz\_Daint.bash}.
